---
title: "STATS406-Final-Project-Qiwei-Lin"
author: "Qiwei Lin"
date: "4/26/2020"
header-includes:
- \usepackage{setspace}\doublespacing
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\tableofcontents
\listoftables
\listoffigures
\newpage

# Overview
This reproducibility appendix contains the technical supplement to the content of my final project. External Requirement Section sets up the computing environment by loading packages and preparing the data for analysis. In the Data Processing section, I wrote a function to select observations of interest and to recode variables from the dataset. In the Checks on Missing Pattern and Descriptive Statistics section, I computed the proportion of missing for variables of interest and calculated some descriptive statistics. The Simulations section contains the result of all my simulation studies. The Analysis section includes all model-fitting, bootstrap and additional calculations for the results I presented in the Analysis section of the paper.

# External Requirement

```{r External Requirement, warning=F}
# load relevant packages
library(tidyverse)
library(mice)
library(boot)
library(foreign)
library(pander)
library(DescTools)
library(pastecs)
library(lme4)
library(plyr)
```

```{r}
# read in the original dataset
CD.data <- read.dta("CDIR61FL.dta")
```


# Data Preprocessing

```{r}
# new names for variables
main_variable = c("caseid", "country", "year","province","old_province",
                  "urban","emo_vio", "phy_vio", "sex_vio","violence", 
                  "marriage", "union1","union2","age", "education", 
                  "wealth_index", "owning_house","owning_land", 
                  "owning_property", 
                  "employ_cash",
                  "employment","employ_paid","employ_kind",
                  "employ_mixed", "partner_edu")
# original variable codes
variables = c("caseid","v101","v025", "d104", "d106", "d107", "d108",
              "v133","v190", "v501", "v502","v731", "v741", "v012", 
              "v745a","v745b", "v746", "v715", "snprovin")
# this function will only select women in union 
# and recode relevant variables, and return the processed dataset
process <- function(df, var, ctry, yr, percent = 0.1, seed = 1234){
  variables <- variables[variables %in% names(df)]
  df <- df %>% select(variables)
  if (percent != 1){
  set.seed(seed)
  n_row <- nrow(df)
  sample_id = sample(n_row, floor(percent*n_row))
  df = df %>% slice(sample_id)
  }
  df$country <- ctry
  df$year <- yr
#---individual level features---#
  df$union1 = ifelse(df$v502 == 1, 1, 0)
  df$union2 = ifelse(grepl(pattern = "currently",x = df$v502), 1, 0) #%>% 
                    #as.factor()
  df = df %>% filter(union1 == 1 | union2 == 1)
#---only keep those who are currently in union
  df$old_province = df$v101
  df$province = df$snprovin
  df$urban = ifelse(df$v025 == "urban", 1, 0) #%>% as.factor()
  df$emo_vio = ifelse(df$d104 == "no", 0, 1) #%>% as.factor()
  df$phy_vio = ifelse(df$d106 == "yes" | df$d107 == "yes", 1, 0) #%>% 
                      #as.factor()
  df$sex_vio = ifelse(df$d108 == "no", 0, 1) #%>% as.factor()
  df$violence = ifelse((df$emo_vio == 1 | df$phy_vio == 1) | 
                             (df$sex_vio == 1), 1, 0) #%>% as.factor()
  df$marriage = ifelse(df$v501 == "married", 1, 0) #%>% as.factor()
  df$union1 = ifelse(df$v502 == 1, 1, 0)
  df$union2 = ifelse(grepl(pattern = "currently",x = df$v502), 1, 0) #%>% 
                    #as.factor()
  df$age = as.numeric(df$v012)
  df$education = df$v133
  df$education[which(df$education == 99)] = NA
  df$wealth_index = df$v190
  
  df$wealth_index = recode_factor(df$v190, `1` = "poorest", 
                                  `2` = "poorer", `3` = "middle", 
                                  `4` = "richer", `5` = "richest",
                                  .ordered = T) %>% unclass() %>%
                                        as.numeric()
  # owning property
  df$owning_house = ifelse(df$v745a != "does not own", T, F) 
  df$owning_land = ifelse(df$v745b != "does not own", T, F) 
  df$owning_property = ifelse(df$owning_house | df$owning_land, 1, 0)
  df$employment = ifelse(df$v731 != "no", 1, 0) 

  df$employ_paid = ifelse(is.na(df$employment), NA, ifelse(df$v741 %in% 
                              c("cash only","cash and in-kind",
                                "in-kind only"), 1, 0)) 
  df$employ_cash = ifelse(is.na(df$employment), NA, ifelse(df$v741 %in% 
                            c("cash only","cash and in-kind"), 1, 0)) 
                             
  df$employ_kind = ifelse(is.na(df$employment), NA, 
                          ifelse(df$v741 %in% c("in-kind only",
                                         "cash and in-kind"), 1, 0))
  df$employ_mixed = ifelse(is.na(df$employment), NA, 
                           ifelse(df$v741 %in% 
                                    c("cash and in-kind"), 1, 0))
#---partner characteristics
  df$partner_edu = df$v715
  df$partner_edu[which(df$partner_edu == 98)] = NA
  processed_data <- df %>% select(main_variable) 
  
  return(processed_data)
}
```

```{r}
CD <- process(CD.data, var = variables,"CD", "2013", percent = 1)
```

# Checks on Missing Pattern and Descriptive Statistics

```{r}
# checks on missing patterns
missing <- CD %>% select(violence, sex_vio, emo_vio,
                         phy_vio, employ_paid,owning_property,
                         wealth_index, 
                         partner_edu, urban,age, education, province)%>%
  md.pairs(.) 

(missing$mm)/nrow(CD)
```

```{r}
# descriptive statistics
CD %>% 
  select(violence,sex_vio, emo_vio, phy_vio,employ_paid,
         owning_property, wealth_index, 
         partner_edu, urban,age, education) %>%   
  summary()
```

```{r}
# calculate standard deviation
CD %>% 
  select(violence,sex_vio, emo_vio, phy_vio,employ_paid,
         owning_property, wealth_index, 
         partner_edu, urban,age, education, province) %>%   
  apply(2,sd,na.rm = T)
```

```{r}
# calculate proportion for each household wealth category
(mean_by_group <- map(.x = 1:5, .f = ~ mean(CD$wealth_index == .x)))
```

```{r}
# calculate standard deviation for each household wealth category
(sd_by_group <- map(.x = 1:5, .f = ~ sd(CD$wealth_index == .x)))
```


## Prepare Two Datasets

```{r}
CD_complete <- CD %>% filter(!is.na(CD$violence)) %>% 
  select(violence,employ_paid,owning_property, wealth_index, 
         partner_edu, urban,age, education, province) %>% na.omit()
CD_extreme <- CD %>% 
  mutate(violence = ifelse(is.na(CD$violence), 1, CD$violence)) %>% 
  select(violence,employ_paid,owning_property, wealth_index, 
         partner_edu, urban,age, education, province) %>% na.omit()
```

## Exploratory Analysis

```{r}
ggplot(CD_complete, 
       aes(ifelse(employ_paid, "Yes", "No"),
           fill = ifelse(violence == 1, "Yes", "No"))) + 
  geom_bar() + 
  labs(x = "Womens Who are Employed and Paid", 
       fill = "Experience\nViolence")

ggplot(CD_extreme, 
       aes(ifelse(employ_paid, "Yes", "No"),
           fill = ifelse(violence == 1, "Yes", "No"))) + 
  geom_bar() + 
  labs(x = "Womens Who are Employed and Paid", 
       fill = "Experience\nViolence")
```

```{r}
ggplot(CD_complete, 
       aes(ifelse(owning_property, "Yes", "No"),
           fill = ifelse(violence == 1, "Yes", "No"))) + 
  geom_bar() + 
  labs(x = "Womens Who Own Either House Or Land", 
       fill = "Experience\nViolence")

ggplot(CD_extreme, 
       aes(ifelse(owning_property, "Yes", "No"),
           fill = ifelse(violence == 1, "Yes", "No"))) + 
  geom_bar() + 
  labs(x = "Womens Who Own Either House Or Land", 
       fill = "Experience\nViolence")
```


```{r}
ggplot(CD_complete, 
       aes(recode_factor(wealth_index, "1" = "poorest", 
                         "2" = "poorer", "3" = "middle", 
                         "4" = "richer", "5" = "richest",.ordered = T),
           fill = ifelse(violence == 1, "Yes", "No"))) + 
  geom_bar() + 
  labs(x = "Women's Household Wealth Index", 
       fill = "Experience\nViolence")

ggplot(CD_extreme, 
       aes(recode_factor(wealth_index, "1" = "poorest", 
                         "2" = "poorer", "3" = "middle", 
                         "4" = "richer", "5" = "richest",.ordered = T),
           fill = ifelse(violence == 1, "Yes", "No"))) + 
  geom_bar() + 
  labs(x = "Women's Household Wealth Index", 
       fill = "Experience\nViolence")
```



```{r}
ggplot(CD_complete, 
       aes(education,fill = ifelse(violence == 1, "Yes", "No"))) + 
  geom_density(alpha = 0.5) + 
  labs(x = "Women's Years of Education", 
       fill = "Experience\nViolence")

ggplot(CD_extreme, 
       aes(education,fill = ifelse(violence == 1, "Yes", "No"))) + 
  geom_density(alpha = 0.5) + 
  labs(x = "Women's Years of Education", 
       fill = "Experience\nViolence")
```


# Simulations

## Chi-squared Test and G^2 Test and Difference-in-Proportion

```{r}
set.seed(406,sample.kind = "Rounding")
# Type I error rate
k <- 10000
chisq_ps <- replicate(k, {
    chisq.test(x = rbinom(1000, 1, 0.5), 
               y = rbinom(1000, 1, 0.5))$p.value
})

df_in_prop_ps <- replicate(k, {
  prop.test(x = c(sum(rbinom(1000, 1, 0.5)),
                  sum(rbinom(1000, 1, 0.5))),
            n = c(1000,1000))$p.value
})


LR_chisq_ps <- replicate(k, {
    GTest(x = rbinom(1000, 1, 0.5), y = rbinom(1000, 1, 0.5))$p.value
})
```

```{r}
chisq_size <- binom.test(x = sum(chisq_ps <= 0.05), n = k,
                         conf.level = 0.95)
chisq_size$conf.int
chisq_size$estimate

df_in_prop_size <- binom.test(x = sum(df_in_prop_ps <= 0.05), 
                              n = k,conf.level = 0.95)
df_in_prop_size$conf.int
df_in_prop_size$estimate

LR_chisq_size <- binom.test(x = sum(LR_chisq_ps <= 0.05), 
                            n = k,conf.level = 0.95)
LR_chisq_size$conf.int
LR_chisq_size$estimate
```

```{r}
chisq_ps_alt <- replicate(k, {
  F_dist = rbinom(1000, 1 , 0.5)
  G_dist = rbinom(1000, 1, prob = ifelse(F_dist == 1, 0.6, 0.5)) 
  chisq.test(x = F_dist, y = G_dist)$p.value
})

df_in_prop_ps_alt <- replicate(k, {
  F_dist = rbinom(1000, 1 , 0.5)
  G_dist = rbinom(1000, 1, prob = ifelse(F_dist == 1, 0.6, 0.5))
  prop.test(x = table(F_dist,G_dist),
            n = c(1000,1000))$p.value
})

LR_chisq_ps_alt <- replicate(k, {
  F_dist = rbinom(1000, 1 , 0.5)
  G_dist = rbinom(1000, 1, prob = ifelse(F_dist == 1, 0.6, 0.5)) 
  GTest(x = F_dist, y = G_dist)$p.value
})
```

```{r}
chisq_power <- binom.test(x = sum(chisq_ps_alt <= 0.05), 
                          n = k,conf.level = 0.95)
chisq_power$conf.int
chisq_power$estimate

df_in_prop_power <- binom.test(x = sum(df_in_prop_ps_alt <= 0.05), 
                               n = k,conf.level = 0.95)
df_in_prop_power$conf.int
df_in_prop_power$estimate

LR_chisq_power <- binom.test(x = sum(LR_chisq_ps_alt <= 0.05), 
                            n = k,conf.level = 0.95)
LR_chisq_power$conf.int
LR_chisq_power$estimate
```

## Chi-squared Test, G^2 Test and M^2 Test

```{r}
set.seed(406, sample.kind = "Rounding")
chisq_ps <- replicate(k, {
    chisq.test(x = sample(1:5,size = 1000,replace = T,
                          prob = rep(0.2,5)), 
               y = rbinom(1000, 1, 0.5))$p.value
})

chisq_size <- binom.test(x = sum(chisq_ps <= 0.05), 
                          n = k,conf.level = 0.95)
chisq_size$conf.int
chisq_size$estimate
```

```{r}
G_ps <- replicate(k, {
     GTest(x = sample(1:5,size = 1000,replace = T,
                          prob = rep(0.2,5)), 
           y = rbinom(1000, 1, 0.5))$p.value
})

G_size <- binom.test(x = sum(G_ps <= 0.05), 
                          n = k,conf.level = 0.95)
G_size$conf.int
G_size$estimate
```

I did not find any existing function or package in R that calculate $M^2$. The function below is obtained from the online resource page of the Department of Statistics at the Pennsylvania State University (https://online.stat.psu.edu/stat504/node/91/). I modified this function by changing variable names and adding the calculation of p-value.

```{r}
pears.cor = function(table, row_score, col_score){ 
	dim=dim(table) 
	rbar=sum(margin.table(table,1)*row_score)/sum(table) 
	rdif=row_score-rbar 
	cbar=sum(margin.table(table,2)*col_score)/sum(table) 
	cdif=col_score-cbar 
	ssr=sum(margin.table(table,1)*(rdif^2)) 
	ssc=sum(margin.table(table,2)*(cdif^2)) 
	ssrc=sum(t(table*rdif)*cdif) 
	pcor=ssrc/(sqrt(ssr*ssc)) 
	pcor 
	M2=(sum(table)-1)*pcor^2
	M2
	p.values = 1 - pchisq(q = M2,df =1)
	p.values
	result=c(pcor, M2, p.values)
	result
}
```


```{r}
M2_ps <- replicate(k, {
    x = sample(1:5,size = 1000,replace = T,prob = rep(0.2,5)) 
    y = rbinom(1000, 1, 0.5)
    pears.cor(table(x,y), row_score = c(1:5), col_score = c(0,1))[3]
})

M2_size <- binom.test(x = sum(M2_ps <= 0.05), 
                          n = k,conf.level = 0.95)
M2_size$conf.int
M2_size$estimate
```

```{r}
prob = c(0.6,0.55,0.5,0.45,0.4)
chisq_ps_alt <- replicate(k, {
  x = sample(1:5,size = 1000,replace = T,
                        prob = c(0.1,0.25,0.3,0.25,0.1))
  y = rbinom(1000, 1, prob = prob[x])
  test <- chisq.test(table(x,y))
  test$p.value
})
chisq_power <- binom.test(x = sum(chisq_ps_alt <= 0.05), 
                          n = k,conf.level = 0.95)
chisq_power$estimate
chisq_power$conf.int
```

```{r}
prob = c(0.6,0.55,0.5,0.45,0.4)
G_ps_alt <- replicate(k, {
  x = sample(1:5,size = 1000,replace = T,
                        prob = c(0.1,0.25,0.3,0.25,0.1))
  y = rbinom(1000, 1, prob = prob[x])
  test <- GTest(table(x,y))
  test$p.value
})
G_power <- binom.test(x = sum(G_ps_alt <= 0.05), 
                          n = k,conf.level = 0.95)
G_power$estimate
G_power$conf.int
```


```{r}
prob = c(0.6,0.55,0.5,0.45,0.4)
M2_ps_alt <- replicate(k, {
  x = sample(1:5,size = 1000,replace = T,
                        prob = c(0.1,0.25,0.3,0.25,0.1))
  y = rbinom(1000, 1, prob = prob[x])
  pears.cor(table(x,y), row_score = c(1:5), col_score = c(0,1))[3]
})
M2_power <- binom.test(x = sum(M2_ps_alt <= 0.05), 
                          n = k,conf.level = 0.95)
M2_power$estimate
M2_power$conf.int
```

## Simulation of the Bias of Logistic Regression Coefficient Estimates and Bootstrap Confidence Interval Coverage Rate

```{r}
set.seed(406, sample.kind = "Rounding")
b0 <- 1
b1 <- 2
true_betas <- c(b0,b1)

mu <- function(x){
  xb <- (b0 + b1*x)
  mu <- exp(xb)/(1 + exp(xb))
}
x <- runif(1000, 0, 5)
y <- rbinom(1000, 1, mu(x))
df <- data.frame(x = x, y = y)
```

```{r}
k <- 2000
bias <- as.data.frame(replicate(n = k, {
    x <- runif(1000, 0, 5)
    y <- rbinom(1000, 1, mu(x))
    df <- data.frame(x = x, y = y)
    fit = glm(y ~ x, data = df, family = binomial(link = "logit"))
    betas <- coef(fit)
    bias <- betas - true_betas
}))

CI <- apply(bias, MARGIN = 1, FUN = quantile,probs = c(0.005, 0.995))
# gather all quantities of interest for plotting 
beta_bias <- data.frame(betas = c("Beta0","Beta1"),
                        bias_mean = apply(bias, 1, mean),
                        bias_lwr = CI[1,],
                        bias_upr = CI[2,])
# plot the 99% CI for bias
ggplot(beta_bias, aes(betas, bias_mean)) + geom_point() + 
       geom_errorbar(aes(ymin=bias_lwr, 
                         ymax=bias_upr), width=.1) + 
       labs(x = "Betas",y = "Bias")
```


```{r}
# bootstrap for coefficients
bootsteps = 1000

b0_extract <- function(df, index){
  df_star <- df[index, ]
  coef(glm(y ~ x, data = df_star, family = binomial(link = "logit")))[1]
}

b1_extract <- function(df, index){
  df_star <- df[index, ]
  coef(glm(y ~ x, data = df_star, family = binomial(link = "logit")))[2]
}

# calculate coverage rate 
coverage_b0 <- rep(0, 100)
coverage_b1 <- rep(0, 100)
for(i in 1:100){
  beta0_boot <- boot(df, b0_extract, R = bootsteps)
  beta0_ci <- beta0_boot %>% boot.ci(type = c("perc"))
  coverage_b0[i] <- between(b0, beta0_ci$percent[4],
                            beta0_ci$percent[5])
}

for(i in 1:100){
  beta1_boot <- boot(df, b1_extract, R = bootsteps)
  beta1_ci <- beta1_boot %>% boot.ci(type = c("perc"))
  coverage_b1[i] <- between(b1, beta1_ci$percent[4],
                            beta1_ci$percent[5])
}
```

```{r}
binom.test(x = sum(coverage_b0), n = 100,conf.level = 0.95)
binom.test(x = sum(coverage_b1), n = 100,conf.level = 0.95)
```


# Analysis

## Permutation Test on Women's Employment Status and Experience of IPV 

```{r, warning=F}
set.seed(406, sample.kind = "Rounding")
dist.t.complete <- replicate(1000,{
  # shuffle the employ_paid label
  permuted_emp_paid <- sample(CD_complete$employ_paid, 
                              size = nrow(CD_complete), 
                              replace = F)
  GTest(x = permuted_emp_paid, y = CD_complete$violence)$statistic
})

(t_observed.complete <- GTest(x = CD_complete$employ_paid, 
                              y = CD_complete$violence)$statistic)
(p <- 2 * min(mean(dist.t.complete <= t_observed.complete), 
              mean(dist.t.complete >= t_observed.complete))) 
```


```{r}
dist.t <- replicate(1000,{
  # shuffle the employ_paid label
  permuted_emp_paid <- sample(CD_extreme$employ_paid, 
                              size = nrow(CD_extreme), 
                              replace = F)
  GTest(x = permuted_emp_paid, y = CD_extreme$violence)$statistic
})

(t_observed <- GTest(x = CD_extreme$employ_paid, 
                     y = CD_extreme$violence)$statistic)
(p <- 2 * min(mean(dist.t <= t_observed), mean(dist.t >= t_observed))) 
```

## Permutation Test on Women's Property Ownership and Experience of IPV 

```{r}
dist.t.complete <- replicate(1000,{
  # shuffle the owning property label
  permuted_own_prop <- sample(CD_complete$owning_property, 
                              size = nrow(CD_complete), 
                              replace = F)
  GTest(x = permuted_own_prop, y = CD_complete$violence)$statistic
})

(t_observed.complete <- GTest(x = CD_complete$owning_property, 
                              y = CD_complete$violence)$statistic)
(p <- 2 * min(mean(dist.t.complete <= t_observed.complete), 
              mean(dist.t.complete >= t_observed.complete))) 
```


```{r}
dist.t.extreme <- replicate(1000,{
  # shuffle the owning property label
  permuted_own_prop <- sample(CD_extreme$owning_property, 
                              size = nrow(CD_extreme), 
                              replace = F)
  GTest(x = permuted_own_prop, y = CD_extreme$violence)$statistic
})

(t_obs_extreme <- GTest(x = CD_extreme$owning_property, 
                        y = CD_extreme$violence)$statistic)
(p <- 2 * min(mean(dist.t.extreme <= t_obs_extreme), 
              mean(dist.t.extreme >= t_obs_extreme))) 
```



## Permutation Test on Women's Household Wealth and Experience of IPV 

```{r}
dist.t.complete <- replicate(1000,{
  # shuffle the wealth_index label
  permuted_wealth_idx <- sample(CD_complete$wealth_index, 
                              size = nrow(CD_complete), 
                              replace = F)
  pears.cor(table(permuted_wealth_idx,CD_complete$violence), 
            row_score = c(1:5), col_score = c(0,1))[2]
})

(t_observed.complete <- pears.cor(table(CD_complete$wealth_index,
                                        CD_complete$violence), 
                                  row_score = c(1:5), 
                                  col_score = c(0,1))[2])
(p <- 2 * min(mean(dist.t.complete <= t_observed.complete), 
              mean(dist.t.complete >= t_observed.complete))) 
```

```{r}
dist.t.extreme <- replicate(1000,{
  # shuffle the wealth_index label
  permuted_wealth_idx <- sample(CD_extreme$wealth_index, 
                              size = nrow(CD_extreme), 
                              replace = F)
  pears.cor(table(permuted_wealth_idx,CD_extreme$violence), 
            row_score = c(1:5), col_score = c(0,1))[2]
})

(t_observed.extreme <- pears.cor(table(CD_extreme$wealth_index,
                                        CD_extreme$violence), 
                                  row_score = c(1:5), 
                                  col_score = c(0,1))[2])
(p <- 2 * min(mean(dist.t.extreme <= t_observed.extreme), 
              mean(dist.t.extreme >= t_observed.extreme))) 
```

## Logistic Regression

```{r}
fit1 <- glm(violence ~ employ_paid+ owning_property + 
              wealth_index + education  + partner_edu + urban + age, 
            data = CD_complete, 
              family = binomial(link = "logit"))
summary(fit1)
```

```{r}
fit2 <- glm(violence ~ employ_paid+ owning_property + 
              wealth_index + education  + partner_edu + urban + age, 
            data = CD_extreme, 
              family = binomial(link = "logit"))
summary(fit2)
```

## Bootstrap

```{r}
bs1 <- function(df, index) {
  df_star <- df[index,] # allows boot to select sample
  refitted.mod <- update(fit1, data=df_star)
  coef(refitted.mod)
  return(coef(refitted.mod))
}

results1 <- boot(data=CD_complete, statistic = bs1, 
                 strata = CD_complete$province, R=1000)
map(.x = 1:8, .f = ~ boot.ci(results1, type="perc", index=.x))
```


```{r}
bs2 <- function(df, index) {
  df_star <- df[index,] # allows boot to select sample
  refitted.mod <- update(fit2, data=df_star)
  coef(refitted.mod)
  return(coef(refitted.mod))
}

results2 <- boot(data=CD_extreme, statistic = bs2,
                 strata = CD_extreme$province, R=1000)
map(.x = 1:8, .f = ~ boot.ci(results2, type="perc", index=.x))
```

## Calculating Changes in Predicted Probability

```{r}
# calculate changes in prob due to employment status
simulated_women_emp = data.frame(
  employ_paid = 1, age = 30, education = 5, partner_edu = 9, urban = 0,
  wealth_index = 3, owning_property = 1
)

simulated_women_unemp = data.frame(
  employ_paid = 0, age = 30, education = 5, partner_edu = 9, urban = 0,
  wealth_index = 3, owning_property = 1
)
predict(fit1, newdata = data.frame(simulated_women_emp),
        type = "response") - 
  predict(fit1, newdata = data.frame(simulated_women_unemp),
          type = "response") 
```



```{r}
# calculate changes in prob due to property ownership
simulated_women_own = data.frame(
  employ_paid = 1, age = 30, education = 5, partner_edu = 9, urban = 0,
  wealth_index = 3, owning_property = 1
)

simulated_women_not_own = data.frame(
  employ_paid = 1, age = 30, education = 5, partner_edu = 9, urban = 0,
  wealth_index = 3, owning_property = 0
)
predict(fit1, newdata = data.frame(simulated_women_own),
        type = "response") - 
  predict(fit1, newdata = data.frame(simulated_women_not_own),
          type = "response") 
```

```{r}
predict(fit2, newdata = data.frame(simulated_women_own),
        type = "response") - 
  predict(fit2, newdata = data.frame(simulated_women_not_own),
          type = "response")
```

```{r}
# calculate changes in prob due to household wealth
sim_women_poorest = data.frame(
  employ_paid = 1, age = 30, education = 5, partner_edu = 9, urban = 0,
  wealth_index = 1, owning_property = 1
)

sim_women_poorer = data.frame(
  employ_paid = 1, age = 30, education = 5, partner_edu = 9, urban = 0,
  wealth_index = 2, owning_property = 1
)
predict(fit1, newdata = data.frame(sim_women_poorer),
        type = "response") - 
  predict(fit1, newdata = data.frame(sim_women_poorest),
          type = "response")
```

